Titre

### 2021-05-21 Mes papiers/CR-CVD/CVD_para.tex

In this study, we use a homebuilt confocal microscope that comprises a 1mW green laser, an objective with a numerical aperture of 0.25 to focus the laser onto the sample as well as to collect the NV photoluminescence (PL). The PL was filtered from the green laser using a dichroic mirror and a notch filter. It was then coupled to a multimode fiber and detected by an avalanche photodiode. The magnetic field scans were realized using a C-shaped electromagnet driven by a current generator (HP 33120A).  We then monitor the NV PL synchronously with the changes in the magnetic field.
\begin{figure}[ht]
\centering
{\includegraphics[width=\linewidth]{Scans_fig4}}
\caption{Optical detection of cross-relaxations. {Top}: NV$^-$ photoluminescence counts as a function of the magnetic field amplitude along the [100] crystalline direction (plain line) and fourth-order polynomial fit (dashed line). {Bottom} Curve obtained by subtracting the polynomial fit to the above signal (circles). The simulated cross-relaxations positions are shown by the green dashed, vertical lines. Gaussian fits to the second and third dips are shown by plain orange lines.}
\label{scan}
\end{figure}
Contrary to the more commonly employed $[ 111 ]$ direction, we scan the magnetic field along the diamond $[100]$ crystalline direction. 
Looking at the diamond structure (bottom right in Fig.  \ref{fig1}), it can be noticed that, in this direction, the projections of NV centers (or any other $C_{3v}$ defect) along the magnetic field are identical. This means the transition energies of the different classes of NV centers cannot cross under a B field scan along this direction. This could otherwise result in several low field PL features under arbitrary angles \cite{van_oort_optically_1991, akhmedzhanov_magnetometry_2019} that could mask cross-relaxation from other species and also reduce the CR contrast (see section 4 of the Supplementary Materials for data showing scans along the [111] direction). 
The downside of this choice of the [100] direction is that at large amplitudes, the transverse component of the magnetic field depolarizes all classes of NVs, thus limiting the magnetic field range that can be employed and restricting this detection method to paramagnetic defects with zero-field splittings close to the NV center's.

@@

Fig. \ref{scan} shows the PL as a function of magnetic field amplitude along the $[ 100 ]$ direction, in the 15~G to 145~G range. 
Calibration of the magnetic field amplitude was realized by applying microwave signals at varying frequencies in 2 MHz steps on several magnetic field scans. The microwave induced PL features in the scan are then used to relate the magnetic field to the applied voltage. 
Three features appear in this spectrum : at 20~G,  56~G and 122~G. 
Data averaging was done for 24 hours, but the features appear already with a signal to noise ratio greater than 1 after 10 minutes.  
We also observe an overall drop of the PL as a result of state mixing in the optically excited state \cite{DOHERTY20131}. 
To let the three salient features detach better from the spectrum, we fitted a 4th-order polynomial to the PL evolution, without the spectral bumps, and subtract it from the data. Further details on the fitting choices are provided in Sec.V of the Supplementary material.

In order to attribute the three features to their respective defects, we run a similar scan (Section 1 in the Supplementary Materials) on a type Ib electron irradiated HPHT diamond crystal with a NV concentration in the 5-20 ppm range. Only the first feature appeared. 
This observation guided us to search for CVD-related defects as candidates for the last two features. Paramagnetic defects in CVD-grown diamonds have been extensively studied using EPR  \citep{Ashfold}. These studies demonstrate that hydrogen-related complex such as NVH, VH, VH2 can be stable in diamond. Although their compositions is not always known, several zero-field splittings $D$ can be found in the literature.
Given the small difference between the NV transitions and the observed features, we only concentrate on reported defects with ZFS that are close to the NV$^-$.
The middle column of table \ref{table}, shows the zero-field splitting for two such spin-1 defects found in \citep{cruddace2007magnetic}, namely the negatively charged hydrogen-vacancy (VH$^-$) and WAR1 defects. The latter was analyzed in EPR but its exact structure is unknown \citep{cruddace2007magnetic}.
\begin{table}[htbp]
\centering
\caption{\bf Zero-field splitting parameter $D$ for the spin-1 species in our sample}
\begin{tabular}{ccc}
\hline
$D_z$ estimation (MHz) & Cruddace's work\citep{cruddace2007magnetic} & Our work \\
\hline
NV$^-$ & 2872(7) & * \\
VH$^-$ & 2706(30) & 2694(5)  \\
WAR1 & 2466(60) & 2470(10) \\
\hline
\end{tabular}
  \label{table}
\end{table}
Fig. \ref{energy-levels} shows the frequencies of the NV$^-$, the VH$^-$ and WAR1 spin transitions as a function of the magnetic field amplitude along the $[100]$ direction. Since the NV$^-$ and VH$^-$ are $C_{3v}$ defects, and the WAR1 is a pseudo-$C_{3v}$ defect \citep{cruddace2007magnetic}, all possible orientations are degenerate at this magnetic field orientation, giving only two lines corresponding to the $\ket{0} \to \ket{+1}$ and $\ket{0} \to \ket{-1}$ transitions. The points were the NV levels cross the other defects can give rise to cross-relaxation.

Using this theoretical calculations, we find that the second peak in Fig. \ref{scan} coincides very well with a CR that would occur at the crossing between the $|m_s=0\rangle$ to $|m_s=-1\rangle$ NV transition and the $|m_s=0\rangle$ to $|m_s=+1\rangle$ VH$^-$ transition. 
A gaussian fit to the feature in Fig. \ref{scan} enables us to extrapolate a value for $D=2694(5)$MHz that matches that of the VH$^-$ within the error margins indicated in \citep{cruddace2007magnetic}.
The third peak at 122 G would correspond to a spin defect that has a $D=2470(10)$MHz that also matches the one of the WAR1 defect. 
The values of $D$ for these two defects and the error bars from our measurements are included in the table \ref{table}.
The error bars are estimated by taking into account the precision on the NV$^-$ ZFS, on the angle, on the magnetic field calibration and the precision of the fits. 
We obtain a factor of 6 improvement over the precision reported in \citep{cruddace2007magnetic} and attribute the second and third feature to cross relaxation between the NV center and the VH$^-$ and WAR1 defect. Scans along the [111] direction shown in the Supplementary Material also corroborate this conclusion.

\begin{figure}[htbp]
\centering
{\includegraphics[width=\linewidth]{Theorie_CR}}
\caption{Simulated transition energies of the various considered spins as a function of a magnetic field aligned to the [100] axis. The NV centers electronic spin transitions are shown by the plain thick line, the VH$^-$ using dashed lines, the WAR1 using dash-dotted lines and $^{13}$C-NV pair using dotted lines. The amplitudes of the magnetic field where the energy level of the NV center crosses the one of another species are represented by vertical dashed lines.}
\label{energy-levels}
\end{figure}
The remaining broader feature in the spectrum could be coming from dipolar coupling between the spin of NV centers and paramagnetic defects that are present also in HPHT-grown diamonds, such as the substitutional nitrogen, also called $P_1$ centers ($[P_1]\approx 5-20$ ppm in our sample) or the $^{13}$C atoms (natural isotopic abundance [$^{13}$C]= 1\%). 
Using the results from \cite{simanovskaia_sidebands_2013}, we first intended to correlate its spectral position to the transitions of dipolar-coupled NV and $P_1$ centers. 
 $P_1$ centers have a zero-field splitting of only 100 MHz. In order to cross one of the two NV spin transitions at a magnetic field of 20 G, they would then have to be coupled off-resonantly to the spin of nearby NV centers. The resulting pair could then be coupled resonantly to a nearby polarized NV.
The obtained eigenfrequencies of the dipolar coupled P$_1$-NV pair that we extracted were all inconsistent with the spectral positions of our observed peak within our spectral resolution error ($\approx$1G) (see Section 3 of the Supplementary Materials). This leads us to consider instead the nuclear spin of the $^{13}$C atoms as the most likely candidate.

The nuclear spin of the $^{13}$C atoms do not have a ZFS and its gyromagnetic factor is four orders of magnitude lower than that of the electron. Here again, in order to give a CR contribution to the spectrum at modest magnetic fields, the nuclear spin of the $^{13}$C would first have to be strongly coupled to an NV center. The resulting pair could then be co-resonant with the spin transitions of a bare NV center, as depicted in Fig. 1. This situation can manifest itself when the nuclear spin of $^{13}$C atoms are a few shells away from the nitrogen-vacancy centers. A strong hyperfine coupling rate of 130 MHz can for instance be reached with a $^{13}$C that is only one shell away from the NV center.  
In contrast, higher order shells have a maximum hyperfine coupling of 15 MHz \cite{smeltzer201113c} making them hard to distinguish from the inhomogeneous broadening.
The modeling of this interaction is presented in the section 2 of the Supplementary Materials. The dotted lines in Fig. \ref{energy-levels} show the four transition frequencies of the first shell $^{13}$C coupled to an NV center. The crossings between the $|m_s=0\rangle$ to $|m_s=\pm 1\rangle$ NV transition and the four transitions of this  $^{13}$C-NV pair occur at magnetic field values around 20~G. 
We added these four lines to the experimental spectrum shown in Fig. \ref{scan}. A good agreement is found between the magnetic field at which of these four transitions cross the NV and the broad 20~G feature, letting us conclude that it is the result of a CR between an unpolarized $^{13}$C-NV pair and a polarized NV center.

@@

\begin{thebibliography}{27}%

@@

>>>>

In this study, we use a homebuilt confocal microscope that comprises a 1mW green laser, an objective with a numerical aperture of 0.25 to focus the laser onto the sample as well as to collect the NV photoluminescence (PL). The PL was filtered from the green laser using a dichroic mirror and a notch filter. It was then coupled to a multimode fiber and detected by an avalanche photodiode. The magnetic field scans were realized using a C-shaped electromagnet driven by a current generator (HP 33120A).  We then monitor the NV PL synchronously with the changes in the magnetic field.
\begin{figure}[ht]
\centering
{\includegraphics[width=\linewidth]{Scans_fig4}}
\caption{Optical detection of cross-relaxations. {Top}: NV$^-$ photoluminescence counts as a function of the magnetic field amplitude along the [100] crystalline direction (plain line) and fourth-order polynomial fit (dashed line). {Bottom} Curve obtained by subtracting the polynomial fit to the above signal (circles). The simulated cross-relaxations positions are shown by the green dashed, vertical lines. Gaussian fits to the second and third dips are shown by plain orange lines.}
\label{scan}
\end{figure}
Contrary to the more commonly employed $[ 111 ]$ direction, we scan the magnetic field along the diamond $[100]$ crystalline direction. 
Looking at the diamond structure (bottom right in Fig.  \ref{fig1}), it can be noticed that, in this direction, the projections of NV centers (or any other $C_{3v}$ defect) along the magnetic field are identical. This means the transition energies of the different classes of NV centers cannot cross under a B field scan along this direction. This could otherwise result in several low field PL features under arbitrary angles \cite{van_oort_optically_1991, akhmedzhanov_magnetometry_2019} that could mask cross-relaxation from other species and also reduce the CR contrast (see section 4 of the Supplementary Materials \cite{SM_CR_CVD} (SM) for data showing scans along the [111] direction). \nocite{simanovskaia_sidebands_2013, alvarez_local_2015, jiang2018estimation, kamp2018continuous, Alfasi, lazda2020cross, TALLAIRE2020421}
The downside of this choice of the [100] direction is that at large amplitudes, the transverse component of the magnetic field depolarizes all classes of NVs, thus limiting the magnetic field range that can be employed and restricting this detection method to paramagnetic defects with zero-field splittings close to the NV center's.

@@

Fig. \ref{scan} shows the PL as a function of magnetic field amplitude along the $[ 100 ]$ direction, in the 15~G to 145~G range. 
Calibration of the magnetic field amplitude was realized by applying microwave signals at varying frequencies in 2 MHz steps on several magnetic field scans. The microwave induced PL features in the scan are then used to relate the magnetic field to the applied voltage. 
Three features appear in this spectrum : at 20~G,  56~G and 122~G. 
Data averaging was done for 24 hours, but the features appear already with a signal to noise ratio greater than 1 after 10 minutes.  
We also observe an overall drop of the PL as a result of state mixing in the optically excited state \cite{DOHERTY20131}. 
To let the three salient features detach better from the spectrum, we fitted a 4th-order polynomial to the PL evolution, without the spectral bumps, and subtract it from the data. Further details on the fitting choices are provided in Sec.V of the SM \cite{SM_CR_CVD}.

In order to attribute the three features to their respective defects, we run a similar scan (Section 1 in the SM \cite{SM_CR_CVD}) on a type Ib electron irradiated HPHT diamond crystal with a NV concentration in the 5-20 ppm range. Only the first feature appeared. 
This observation guided us to search for CVD-related defects as candidates for the last two features. Paramagnetic defects in CVD-grown diamonds have been extensively studied using EPR  \citep{Ashfold}. These studies demonstrate that hydrogen-related complex such as NVH, VH, VH2 can be stable in diamond. Although their compositions is not always known, several zero-field splittings $D$ can be found in the literature.
Given the small difference between the NV transitions and the observed features, we only concentrate on reported defects with ZFS that are close to the NV$^-$.
The middle column of table \ref{table}, shows the zero-field splitting for two such spin-1 defects found in \citep{cruddace2007magnetic}, namely the negatively charged hydrogen-vacancy (VH$^-$) and WAR1 defects. The latter was analyzed in EPR but its exact structure is unknown \citep{cruddace2007magnetic}.
\begin{table}[htbp]
\centering
\caption{\bf Zero-field splitting parameter $D$ for the spin-1 species in our sample}
\begin{tabular}{ccc}
\hline
$D_z$ estimation (MHz) & Cruddace's work\citep{cruddace2007magnetic} & Our work \\
\hline
NV$^-$ & 2872(7) & * \\
VH$^-$ & 2706(30) & 2694(5)  \\
WAR1 & 2466(60) & 2470(10) \\
\hline
\end{tabular}
  \label{table}
\end{table}
Fig. \ref{energy-levels} shows the frequencies of the NV$^-$, the VH$^-$ and WAR1 spin transitions as a function of the magnetic field amplitude along the $[100]$ direction. Since the NV$^-$ and VH$^-$ are $C_{3v}$ defects, and the WAR1 is a pseudo-$C_{3v}$ defect \citep{cruddace2007magnetic}, all possible orientations are degenerate at this magnetic field orientation, giving only two lines corresponding to the $\ket{0} \to \ket{+1}$ and $\ket{0} \to \ket{-1}$ transitions. The points were the NV levels cross the other defects can give rise to cross-relaxation.

Using this theoretical calculations, we find that the second peak in Fig. \ref{scan} coincides very well with a CR that would occur at the crossing between the $|m_s=0\rangle$ to $|m_s=-1\rangle$ NV transition and the $|m_s=0\rangle$ to $|m_s=+1\rangle$ VH$^-$ transition. 
A gaussian fit to the feature in Fig. \ref{scan} enables us to extrapolate a value for $D=2694(5)$MHz that matches that of the VH$^-$ within the error margins indicated in \citep{cruddace2007magnetic}.
The third peak at 122 G would correspond to a spin defect that has a $D=2470(10)$MHz that also matches the one of the WAR1 defect. 
The values of $D$ for these two defects and the error bars from our measurements are included in the table \ref{table}.
The error bars are estimated by taking into account the precision on the NV$^-$ ZFS, on the angle, on the magnetic field calibration and the precision of the fits. 
We obtain a factor of 6 improvement over the precision reported in \citep{cruddace2007magnetic} and attribute the second and third feature to cross relaxation between the NV center and the VH$^-$ and WAR1 defect. Scans along the [111] direction shown in the SM \cite{SM_CR_CVD} also corroborate this conclusion.

\begin{figure}[htbp]
\centering
{\includegraphics[width=\linewidth]{Theorie_CR}}
\caption{Simulated transition energies of the various considered spins as a function of a magnetic field aligned to the [100] axis. The NV centers electronic spin transitions are shown by the plain thick line, the VH$^-$ using dashed lines, the WAR1 using dash-dotted lines and $^{13}$C-NV pair using dotted lines. The amplitudes of the magnetic field where the energy level of the NV center crosses the one of another species are represented by vertical dashed lines.}
\label{energy-levels}
\end{figure}
The remaining broader feature in the spectrum could be coming from dipolar coupling between the spin of NV centers and paramagnetic defects that are present also in HPHT-grown diamonds, such as the substitutional nitrogen, also called $P_1$ centers ($[P_1]\approx 5-20$ ppm in our sample) or the $^{13}$C atoms (natural isotopic abundance [$^{13}$C]= 1\%). 
Using the results from \cite{simanovskaia_sidebands_2013}, we first intended to correlate its spectral position to the transitions of dipolar-coupled NV and $P_1$ centers. 
 $P_1$ centers have a zero-field splitting of only 100 MHz. In order to cross one of the two NV spin transitions at a magnetic field of 20 G, they would then have to be coupled off-resonantly to the spin of nearby NV centers. The resulting pair could then be coupled resonantly to a nearby polarized NV.
The obtained eigenfrequencies of the dipolar coupled P$_1$-NV pair that we extracted were all inconsistent with the spectral positions of our observed peak within our spectral resolution error ($\approx$1G) (see Section 3 of the SM \cite{SM_CR_CVD}). This leads us to consider instead the nuclear spin of the $^{13}$C atoms as the most likely candidate.

The nuclear spin of the $^{13}$C atoms do not have a ZFS and its gyromagnetic factor is four orders of magnitude lower than that of the electron. Here again, in order to give a CR contribution to the spectrum at modest magnetic fields, the nuclear spin of the $^{13}$C would first have to be strongly coupled to an NV center. The resulting pair could then be co-resonant with the spin transitions of a bare NV center, as depicted in Fig. 1. This situation can manifest itself when the nuclear spin of $^{13}$C atoms are a few shells away from the nitrogen-vacancy centers. A strong hyperfine coupling rate of 130 MHz can for instance be reached with a $^{13}$C that is only one shell away from the NV center.  
In contrast, higher order shells have a maximum hyperfine coupling of 15 MHz \cite{smeltzer201113c} making them hard to distinguish from the inhomogeneous broadening.
The modeling of this interaction is presented in the section 2 of the SM \cite{SM_CR_CVD}. The dotted lines in Fig. \ref{energy-levels} show the four transition frequencies of the first shell $^{13}$C coupled to an NV center. The crossings between the $|m_s=0\rangle$ to $|m_s=\pm 1\rangle$ NV transition and the four transitions of this  $^{13}$C-NV pair occur at magnetic field values around 20~G. 
We added these four lines to the experimental spectrum shown in Fig. \ref{scan}. A good agreement is found between the magnetic field at which of these four transitions cross the NV and the broad 20~G feature, letting us conclude that it is the result of a CR between an unpolarized $^{13}$C-NV pair and a polarized NV center.

@@

\begin{thebibliography}{32}%

@@

\bibitem [{SM_()}]{SM_CR_CVD}%
  \href@noop {} {\emph {\bibinfo {title} {See Supplemental Material at [URL
  will be inserted by publisher], which includes Refs. [22-26]}}}\BibitemShut
\bibitem [{\citenamefont {Álvarez}\ \emph {et~al.}(2015)\citenamefont
  {Álvarez}, \citenamefont {Bretschneider}, \citenamefont {Fischer},
  \citenamefont {London}, \citenamefont {Kanda}, \citenamefont {Onoda},
  \citenamefont {Isoya}, \citenamefont {Gershoni},\ and\ \citenamefont
  {Frydman}}]{alvarez_local_2015}%
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~A.}\ \bibnamefont
  {Álvarez}}, \bibinfo {author} {\bibfnamefont {C.~O.}\ \bibnamefont
  {Bretschneider}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Fischer}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {London}},
  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Kanda}}, \bibinfo
  {author} {\bibfnamefont {S.}~\bibnamefont {Onoda}}, \bibinfo {author}
  {\bibfnamefont {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Gershoni}}, \ and\ \bibinfo {author} {\bibfnamefont
  {L.}~\bibnamefont {Frydman}},\ }\href {\doibase 10.1038/ncomms9456}
  {\bibfield  {journal} {\bibinfo  {journal} {Nat Commun}\ }\textbf {\bibinfo
  {volume} {6}},\ \bibinfo {pages} {8456} (\bibinfo {year} {2015})}\BibitemShut
\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2018)\citenamefont {Jiang},
  \citenamefont {Ye}, \citenamefont {Jiao}, \citenamefont {Huang},\ and\
  \citenamefont {Lv}}]{jiang2018estimation}%
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.-J.}\ \bibnamefont
  {Jiang}}, \bibinfo {author} {\bibfnamefont {J.-F.}\ \bibnamefont {Ye}},
  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Jiao}}, \bibinfo {author}
  {\bibfnamefont {Z.-Y.}\ \bibnamefont {Huang}}, \ and\ \bibinfo {author}
  {\bibfnamefont {H.-J.}\ \bibnamefont {Lv}},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Chinese Physics B}\ }\textbf {\bibinfo
  {volume} {27}},\ \bibinfo {pages} {057601} (\bibinfo {year}
  {2018})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Kamp}\ \emph {et~al.}(2018)\citenamefont {Kamp},
  \citenamefont {Carvajal},\ and\ \citenamefont
  {Samarth}}]{kamp2018continuous}%
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Kamp}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Carvajal}}, \
  and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Samarth}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
  B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo {pages} {045204} (\bibinfo
  {year} {2018})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Lazda}\ \emph {et~al.}(2020)\citenamefont {Lazda},
  \citenamefont {Busaite}, \citenamefont {Berzins}, \citenamefont {Smits},
  \citenamefont {Auzinsh}, \citenamefont {Budker}, \citenamefont {Ferber},\
  and\ \citenamefont {Gahbauer}}]{lazda2020cross}%
  {Lazda}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Busaite}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Berzins}}, \bibinfo
  {author} {\bibfnamefont {J.}~\bibnamefont {Smits}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Auzinsh}}, \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Budker}}, \bibinfo {author} {\bibfnamefont
  {R.}~\bibnamefont {Ferber}}, \ and\ \bibinfo {author} {\bibfnamefont
  {F.}~\bibnamefont {Gahbauer}},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {arXiv preprint arXiv:2007.00473}\ } (\bibinfo {year}

### 2021-05-21 Mes papiers/Review meca/article.tex

\documentclass[a4paper]{report}
\usepackage[french]{babel}
\usepackage[utf8]{inputenc}
\usepackage[]{amsmath}
\usepackage[]{braket} % \bra, \ket etc
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{subcaption} % package pour faire des subfigures
\usepackage{multirow} % package pour multirow/multicolumn
\usepackage{booktabs} % package pour top/mid/bottom rule
\usetikzlibrary{optics}
\usetikzlibrary{shapes}
\usetikzlibrary{fit}

@@

\begin{document}
\tableofcontents
\chapter{Signal et bruit}
  \section{Conventions, définitions}
  \subsection{Transformée de Fourier}
  On prend la définition "du physicien". Soit $s(t)$ un signal, alors ; 
  \begin{align}
  \tilde{s}_1(\omega)&=\int_{-\infty}^{+\infty} s(t) e^{-i\omega t} dt \\
  s(t)&=\int_{-\infty}^{+\infty}\tilde{s}_1(\omega) e^{i\omega t} \dfrac{d\omega}{2\pi}
  \end{align}
  On peut également choisir la convention :
  \begin{align}
  \tilde{s}_2(\nu)&=\int_{-\infty}^{+\infty} s(t) e^{-i2\pi \nu t} dt \\
  s(t)&=\int_{-\infty}^{+\infty}\tilde{s}_2(\nu) e^{i2\pi \nu t} d\nu
  \end{align}
  Et dans ce cas là tu as simplement $\tilde{s}_1(\omega)=\tilde{s}_2(2\pi \nu)$. Par contre les $\sqrt{2\pi}$ on oublie.

  Dans tous les cas, ton spectre à pour dimension $[\tilde{s}]=[s]\cdot[Hz]^{-1}$
  \subsection{Propriétés de la TF}
  \begin{itemize}
  \item Translation : \begin{equation}
  \tilde{f}(t-\tau)[\omega]=e^{-i\omega \tau} \tilde{f}(t)[\omega]
  \end{equation}
  \item Scaling : \begin{equation}
  \tilde{f}(a\cdot t)[\omega]= \dfrac{1}{|a|} \tilde{f}(t)[\dfrac{\omega}{a}]
  \end{equation}
  En particulier, $\tilde{f}(-t)[\omega]=\tilde{f}(t)[-\omega]$. C'est la "time reversibility"
  \item $f$ réelle $\implies$ $\tilde f$ Hermitienne, soit $\tilde f^*(\omega)= \tilde f(-\omega)$
  \item Inversement, si $f$ est hermitienne (donc paire pour une fonction réelle), $\tilde{f}$ est réelle.
  \item Convolution : 
  \begin{equation}
  TF[(f*g)(\tau](\omega)=\tilde{f}(\omega)\tilde{g}(\omega)
  \end{equation}
  \item Auto-corrélation : \begin{align*}
  \tilde S_{ff}(\omega)&=TF[(f(t)*f^*(-t))] \\
  &=TF[f(t)] \cdot TF[f^*(-t)] \\
  &= TF[f(t)] \cdot TF[f(t)]^* \\
  &= |\tilde{f}(\omega)|^2
  \end{align*}

  \end{itemize}
  \subsection{Transformée de Fourier tronquée}
  L'infini c'est long, surtout dans le négatif. Donc expérimentalement on va plutôt utiliser la TF tronquée : 
  \begin{equation}
  \hat{s}(\omega)=\dfrac{1}{\sqrt{T}}\int_{0}^{T} s(t) e^{-i\omega t} dt
  \end{equation}
  \subsection{Transformée de Fourier discrète}
  \subsection{Produit de convolution}
  \begin{equation}
  (f*g)(\tau)=\int_{-\infty}^{+\infty} f(\tau-t) g(t) dt = \int_{-\infty}^{+\infty} f(t) g(\tau-t) dt
  \end{equation}
  \subsection{Fonction d'auto-corrélation}
  La fonction d'auto-corrélation d'un signal est définie comme :
  \begin{equation}
  R_{ss}(t_1,t_2)=\langle s(t_1)s^*(t_2)\rangle
  \end{equation}
  où $\langle ...\rangle$ représente a priori une moyenne d'ensemble.
  Mais nous on aime bien les processus Markovien, donc $R_{ss}$ n'est plus fonction que de $\tau=|t_1-t_2|$. En plus de ça, on fait une petite hypothèse ergodique est la moyenne d'ensemble devient une moyenne temporelle, et on oublie au passage le facteur de normalisation Alors :
  \begin{equation}
  R_{ss}(\tau)=\int_{-\infty}^{+\infty} s(t) s^*(t-\tau)= (s(t)*s^*(-t))(\tau)
  \end{equation}
  Si jamais ton signal est réel, la fonction d'auto-corrélation est paire, donc $R_{ss}(\tau)=R_{ss}(-\tau)$. Si ton signal est complexe c'est un peu plus chiant.

  La \textbf{Fonction d'auto-covariance} c'est simplement la fonction d'auto-corrélation à la quelle tu soustrais $\langle s(t)\rangle ^2$.
  \subsection{Densité spectrale de puissance}
  On peut définir proprement la DSP à partir de la TF tronquée : 
  \begin{equation}
  S_{ss}(\omega)=\lim_{T \to \infty} \langle |\hat{s}(\omega)|^2 \rangle
  \end{equation}
 Or, \begin{align*}
 \langle |\hat{s}(\omega)|^2 \rangle &=\langle \hat{s}(\omega)\hat{s^*}(\omega) \rangle \\
 &=\langle \dfrac{1}{T} \int_{0}^{T} s(t) e^{-i\omega t} dt \int_{0}^{T} s^*(t') e^{i\omega t'} dt' \rangle\\
 &=\dfrac{1}{T} \int_{0}^{T} \int_{0}^{T}\langle s(t)s^*(t') \rangle e^{i\omega(t-t')} dt\; dt'
 \end{align*}
 Et donc tu vois que, en posant $\tau=t-t'$ et en bidouillant un peu les bornes d'intégrations, tu te retrouves avec :
 \begin{equation}
 S_{ss}(\omega)=\int_{-\infty}^\infty R_{ss}(\tau) e^{-i\omega\tau}\,d \tau=\tilde R_{ss}(\omega)=|\tilde s (\omega)|^2
 \end{equation}
 La densité spectrale de puissance est la TF de la fonction d'auto-corrélation (pour un processus Markovien). C'est le théorème de \textbf{Wiener–Khinchin}.

 La version plus sale c'est d'écrire la DSP comme :
 \begin{equation}
 \langle \tilde{s}(\omega) \tilde{s}^*(\omega') \rangle = S_{ss}(\omega)2\pi  \delta(\omega-\omega')
 \end{equation}

 \section{Résolution d'un Michelson}
 Michelson mais ça marche pour toutes les interférences à deux ondes (Ramsay entre autre).

 \subsection{Réponse spectrale}
 On va commencer par la réponse spectrale d'un Micheslon, c'est à dire le rapport des densités spectrales de puissance en entrée ($I_{in}(\omega)$) et en sortie ($I_{out}(\omega)$) de l'interféromètre. On note $A$ les amplitudes correspondantes, et $\tau$ le retard dans l'interféromètre. Alors :
 \begin{equation}
 I_{in}(\omega)=\tilde{A}_{in}(\omega)\tilde{A}_{in}^*(\omega)=|\tilde{A}_{in}(\omega)|^2=|TF[A_{in}(t)](\omega)|^2
 \end{equation}
 et 
 \begin{align*}
I_{out}(\omega)&= |TF[A_{out}(t)](\omega)|^2 \\
 &= |TF[\dfrac{1}{2} (A_{in}(t)+A_{in}(t-\tau)](\omega)|^2 \\
 &= \left|TF[(A_{in}(t)](\omega)\left(\dfrac{1+e^{i\omega \tau}}{2}\right)\right|^2 \\
 &= I_{in}(\omega) \left(\dfrac{1+e^{i\omega \tau}}{2}\right)^2 \\
 &= I_{in}(\omega) \left(\dfrac{1+\cos \omega tau}{2}\right)
 \end{align*}

 Remarque : le 1/2 dans le $A_{out}(t)$ vient du fait que tu as deux séparatrices, qui ajoutent $1/\sqrt{2}$ chacune.

 On trouve donc l'intervalle spectral libre : \begin{equation}
 \Delta \nu = \dfrac{1}{\tau} = \dfrac{(2)l}{c}
 \end{equation}

 En résonnant maintenant en nombre de particules (photon ou autre), en supposant que le flux incident comporte $N$ particules et le flux sortant (flux transmis, ou nombre d'atomes excités dans le cas de Ramsay) est $N_e$, on a tout simplement \begin{equation}
 N_e=N\left(\dfrac{1+\cos \Phi}{2}\right)
 \end{equation}
Avec $\Phi$ le déphasage entre les deux voies.
\subsection{Pouvoir de résolution}
On va maintenant considérer que $N_e$ est une variable aléatoire, chaque particule ayant une chance $p_e=\dfrac{1+\cos \Phi}{2}$ de passer. On a donc :
\begin{align}
\langle N_e\rangle &= N\left(\dfrac{1+\cos \Phi}{2}\right) \\
\Delta^2 N_e &= N(p_e)(1-p_e) = N\dfrac{\sin ^2 \Phi}{4} \\
\Delta N_e &=\sqrt{N} \dfrac{|\sin \Phi|}{2}
\end{align}

Maintenant pour s'intéresser au pouvoir de résolution, on va considérer un résultat $N_{e1}$ de $N$ particules à $\omega$ (où $\Delta$ pour un Ramsay) et un autre résultat $N_{e2}$ de $N$ particules à $\omega + \delta \omega$. Pour pouvoir distinguer le résultat entre les deux pulsations, il faut que la différence des valeurs moyennes soit plus grande que ($\sqrt{2}$ fois) l'écart type du résultat. ($\sqrt{2}$ car il y a deux variables aléatoires dont tu fais la différence, donc tu sommes les variances, un peu comme une mesure à la règle. Mais en vrai c'est du chipotage). D'où : \begin{equation}
\langle N_e (\omega+ \delta \omega)\rangle - \langle N_e (\omega)\rangle \approx -N\tau\dfrac{\sin \omega \tau}{2} \geq \sqrt{2N} \dfrac{\sin \omega \tau}{2} 
\end{equation}

D'où finalement \begin{equation}
\delta \omega \geq \dfrac{\sqrt{2}}{\sqrt{N}\tau}
\end{equation}

On constate que le pouvoir de résolution d'un Michelson ne dépend pas de la phase : Le signal et le bruit sont tous les deux plus importants quand ta phase vaut $\pi/2$

On remarque également qu'on a une limite en $1/\tau$, qui vient de la transformée de Fourier / Heisenberg temps/énergie, et en $1/\sqrt{N}$, qui est la limite "classique" pour tout processus stochastique à N particules. En utilisant des états quantiques à N particules (intriquées donc) on peut idéalement monter à des résolutions en $1/N$.
  \end{document}

>>>>

\documentclass[a4paper]{article}
\usepackage[french]{babel}
\usepackage[utf8]{inputenc}
\usepackage[]{amsmath}
\usepackage[]{braket} % \bra, \ket etc
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{subcaption} % package pour faire des subfigures
\usepackage{multirow} % package pour multirow/multicolumn
\usepackage{booktabs} % package pour top/mid/bottom rule
\usetikzlibrary{optics}
\usetikzlibrary{shapes}
\usetikzlibrary{fit}

@@

\begin{document}
  \pagenumbering{gobble}
  \maketitle
  \newpage
  \pagenumbering{arabic}  
  \tableofcontents
  \newpage
  \section{Introduction}
  \section{Bibliographie} % Ca marche si t'as un fichier biblio.bib dans le même dossier
	\bibliographystyle{plain}
	\bibliography{biblio}
  \end{document}
